Exploring the Motives and Driving Forces Behind Modifications to APIs From a Software Evolution Perspective

### 2015-05-06 thesis/paper.tex
Finished review of RQ1 results

%%Describe the change 
The module axhttp serves to provide a Common Gateway Interface which allows the camera to dynamically send data to web pages. The previous version of axhttp was re-implemented in version 2.0, to correspond with the new design standards. Additional functionality was also added to the module.
%%Relate it to Categories
This change re-implemented an existing module while adhering to the new design of API version 2.0. The main categorisation was chosen to be enhancive with groomative as the secondary change.
%%What she said 
The interviewee expressed that the main driving force behind this change was to re-implement and add new functionality to the axhttp module, while at the same time, allowing them to the module according to the new design.
%%Category based on her information
Our categorisation of enhancive and groomative was therefore correct for this change. The primary intent was to add functionality while also allowing the re-implementation accommodate the new API design.

@@

%%Describe the change 
The parameter setting module of the API allows data and application settings to be saved so that they are not lost when the device is not running. This module was re-implemented as ax\_parameter with added functionality and conformance to the new design standards of API version 2.0.
%2
Given that this change re-implemented an existing module while also incorporating the new design standards, it has been categorised as being primarily enhancive with a secondary category of groomative.
%3
The interviewee clarified that this change was mainly concerned with re-implementing existing functionality while simultaneously adopting the new standards of version 2.0. 
%4
Given the information from the interview, we concluded that this change was correctly categorised; the primary intent was enhancive and the secondary intent was groomative.

@@

%%Describe the change 
The burst mode feature of the API allowed users to buffer a series of images for more exact analysis. This feature was deprecated during the transition between version 1.4 and 2.0 and was not re-implemented.
%%Relate it to Categories
This change presented itself as a clear example of a reductive category of maintenance, as it was simply removed and was not replaced. We also concluded that this change had no secondary category.
%%What she said
The interviewee described that in order to continue using this feature in version 2.0 and in newer versions of the camera hardware, it would have to be re-implemented. An impact assessment was undertaken to determine if the removal of the function would be costly. Ultimately it was deemed appropriate and the function was removed from the API.
%%Category based on her information
Given this information, we can conclude that we correctly categorised this as reductive and that there are indeed no other secondary categories to describe this change.

@@

%%Describe the change 
The case company included a selection of example programs to assist developers with creating applications. This trend continued in 2.0, but there were some significant improvements. The number of example programs increased, as did the amount of comments accompanying the code which has lead to an more robust set of examples.
%%Relate it to Categories
We therefore concluded that this change was updative, as the example code was updated to the new API and the new techniques that it utilises. We further decided that this change also had a secondary category of reformative.
%%What she said
From the interview it became clear that the improvement of the example code was an important change between the two versions. The interviewee described how the examples were used frequently by their customers, however, the old examples varied significantly, even between similar tasks. This ultimately meant that the old examples were not satisfactory and new ones needed to be created, preferably conforming to a standard. The new example code explicitly covered the new functionality, focusing on new features and showing how they can be combined to create applications.
%%Category based on her information
With this information we concluded that our categorisation was incorrect. It became clear that this change was in actual fact primarily reformative, given that the changes to the documentation were being performed to meet the needs of the API users. It was also clear that the subcategory should therefore have been updative.

@@

%%Describe the change 
As the API code was updated in version 2.0, the API documentation was updated to correspond with the new code. While there were no substantial changes, we found that the documentation is no longer offered as a PDF but is instead only offered as HTML. 
%%Relate it to Categories
We categorised this change as being updative with a reformative secondary category for the reasons that the change only updated the documentation to reflect the recent changes in version 2.0.
%%What she said
This sentiment was supported by the interview. The interviewee agreed with our assessment that the documentation was only changed to be up to date with the current workings of the API and how the new systems interact with each other.
%%Category based on her information
As there was no information to contradict our categorisations we have concluded we were correct in our predictions.

@@

%%Describe the change 
Version 1.4 of the API allowed direct access to the headers of each module available in the API. Version 2.0 changed this by including interfaces through which functionality is accessed. This design change has had an effect on the whole API, as it has changed the structure of modules, but not the functionality of them.
%%Relate it to Categories
We therefore concluded that this change would be best categorised as  groomative. The secondary category was categorised as preventive, as this change could be seen as an attempt to reduce future maintenance. 
%%What she said
The interview provided further insight into the reasoning behind this design change. Improvements to the coding standards, the desire for an event driven system and difficulty in using the existing APIs were all contributors to the decision to change the interfaces of the API. Furthermore, the re-design would hopefully avoid future maintenance while allowing the system to be easily extended. 
%%Category based on her information
Taking this information into account, we concluded that our categorisation was incorrect. The interview showed that the primary categorisation should have been preventive, given the strong emphasis on avoiding future maintenance and improving ease of use. We further concluded that the secondary change should have been groomative to reflect the intent to make the API more maintainable.

@@

%%Describe the change 
A substantial change included in version 2.0 was the addition of header files, containing enums of error codes. While we were not aware of what error handling was utilised prior to this version, we assumed it had changed, given the inclusion of these new files.
%%Relate it to Categories
Based on this, we categorised this change as being primarily preventive as error handling is preventive by nature. Groomative was decided as the secondary category of maintenance, as improvement of error handling could be regarded as an attempt to improve maintainability. 
%%What she said
%% Glib - https://developer.gnome.org/glib/
During the interview, it was made clear that the previous error handling was lacking in expressiveness and usability. Glib was added to version 2.0 and the error handling functionality that Glib provides, was incorporated into the new API design.
%%Category based on her information
We therefore concluded that our categorisation for this change was correct. Indeed, the primary reason for the change was to improve the existing error handling while conforming to the new API standard.

>>>>

%%Describe the change 
The module axhttp serves to provide a Common Gateway Interface which allows the camera to dynamically send data to web pages. The previous version of axhttp was re-implemented in version 2.0, to correspond with the new design standards and at the same time, additional functionality was added to the module.
%%Relate it to Categories
This change re-implemented an existing module while adhering to the new design of API version 2.0. The main categorisation therefore was chosen to be enhancive with groomative as the secondary change.
%%What she said 
The interviewee described that the main driving force behind this change was to re-implement and add new functionality to the axhttp module, while at the same time, following the new design.
%%Category based on her information
Our categorisation of enhancive and groomative was therefore correct for this change. The primary intent was to add functionality while also allowing the re-implementation to make use of the new API design.

@@

%%Describe the change 
The parameter setting module of the API allowed data and application settings to be saved so that they are not lost if the device is not running. This module was re-implemented as ax\_parameter with added functionality and conformance to the new design standards of API version 2.0.
%2
Given that this change re-implemented an existing module while also incorporating the new design standards, it has been categorised as being primarily enhancive with a secondary category of groomative.
%3
The interviewee clarified that this change was mainly concerned with re-implementing existing functionality, while simultaneously adopting the new standards of version 2.0. 
%4
Given the information from the interview, we concluded that this change was correctly categorised; the primary intent was enhancive and the secondary intent was groomative.

@@

%%Describe the change 
The burst mode feature of the API allowed users to buffer a series of images for greater analysis. This feature was deprecated during the transition between version 1.4 and 2.0 and was not re-implemented.
%%Relate it to Categories
This change presented itself as a clear example of a reductive category of maintenance, as it was simply removed and was not replaced. We therefore gave no secondary categorisation for this change.
%%What she said
The interviewee described, that in order to continue using this feature, it would have to be re-implemented. An impact assessment was undertaken to determine if the removal of the function would be costly. Ultimately it was deemed appropriate to remove and the function was take out of the API.
%%Category based on her information
We can therefore conclude that we correctly categorised this change as reductive and that there are indeed, no secondary categories to describe this change.

@@

%%Describe the change 
The case company included a selection of example programs to assist developers with creating applications. This trend continued in version 2.0, but there were some significant improvements. The number of example programs and the amount of comments accompanying the code increased, thus improving quality of the examples.
%%Relate it to Categories
We therefore concluded that this change was updative, as the example code was updated to the new API and the new techniques that it utilises. We further decided that this change also had a secondary category of reformative.
%%What she said
During the interview, it became clear that the improvement of the example code was an important change between the two versions. The interviewee described how the examples were used frequently by their customers, however, the old examples had many varied implementation techniques even for similar tasks. This ultimately meant that the old examples were not satisfactory and that new examples would have to be written, preferably conforming to the same standards. The new example code explicitly covered the new functionality, focusing on new features and showing how they can be combined to create applications.
%%Category based on her information
With this information, we concluded that our categorisation was incorrect. It became clear that this change was, in actual fact, primarily reformative. It was also clear that the subcategory should therefore have been updative.

@@

%%Describe the change 
As the API code was updated in version 2.0, the API documentation was updated to correspond with the new code. While there were no substantial changes, we found that the documentation is no longer offered as a PDF but is instead only offered as HTML. 
%%Relate it to Categories
We categorised this change as being updative with a reformative secondary category for the reasons that the change only updated the documentation to reflect the recent changes in version 2.0.
%%What she said
This sentiment was shared by the interviewee. They agreed with our assessment, that the documentation was only changed to keep it up to date with the current workings of the API and how the new systems interact with each other.
%%Category based on her information
We can therefore say that our categorisations were correct, the change was updative and reformative.

@@

%%Describe the change 
Version 1.4 of the API allowed direct access to the headers of each module available in the API. Version 2.0 changed this by including interfaces through which functionality is accessed. This design change has had an effect on the whole API, as it has changed the structure of modules, but not the functionality of them.
%%Relate it to Categories
We therefore concluded that this change would be best categorised as  groomative. The secondary category was categorised as preventive, as the change could be seen as an attempt to reduce future maintenance. 
%%What she said
The interview provided further insight into the reasoning behind this design change. Improvements to coding standards, the desire for an event driven system and difficulty in using the existing APIs were all contributors to the decision to use interfaces in versions 2.0 of the API. Furthermore, the re-design would hopefully avoid future maintenance, while also allowing the system to be easily extended. 
%%Category based on her information
Taking this information into account, we concluded that our categorisation was incorrect. The interview showed that the primary categorisation should have been preventive, given the strong emphasis on avoiding future maintenance and improving usability. We further concluded that the secondary change should have been groomative, to better reflect the intent of improving the APIs maintainability.

@@

%%Describe the change 
A substantial change included in version 2.0 was the addition of header files, containing enums of error codes. While we were not aware of what error handling was utilised prior to this version, we assumed it had changed, given the inclusion of these new files.
%%Relate it to Categories
We therefore categorised this change as being primarily preventive, as error handling is preventive by nature. Groomative was decided as the secondary category of maintenance, as improvement of error handling could be regarded as an attempt to improve maintainability. 
%%What she said
%% Glib - https://developer.gnome.org/glib/
During the interview, it was made clear that the previous error handling was lacking in expressiveness and usability. Glib was added to version 2.0 and the error handling functionality that Glib provides was incorporated into the new API design.
%%Category based on her information
We therefore concluded that our categorisation for this change was correct. Indeed, the primary reason for the change was to improve the existing error handling while conforming to the new API standard.
